Quality Assesment of OpenStreetMap Footpath Data

### 2020-06-11 report/report.tex
Update todo
Update shape accuracy section references
Shorten title

\title{Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation}
\alttitle{Kvalitetiv undersökning av OpenStreetMaps gångvägsdata för stadsmodellering i 3D}
\author{Alexander Hjelm}
\email{aljhelm@kth.se}
\supervisor{Christopher Peters}
\examiner{Jonas Beskow}
%\hostcompany{Företaget AB} % Remove this line if the project was not done at a host company
\programme{Master in Computer Science}
\school{School of Electrical Engineering and Computer Science}
\date{\today}

@@

% TODO: Mention that positional accuracy will be focused on, and the implications of not fixing errors when converting to a 3D model
When it comes to the quality of available data, it turns out that in practise, geodata databases without errors are rare.
Among the most common errors are missing or invalid geometry, and invalid semantics.
However, \textbf{(Biljecki et al, 2016 (2))} note that there are coming more and more sophisticated methods for automatically correcting the most common errors.
Geodata validation and correction is only an emerging field of research.
and many such datasets were usually obtained years ago, and creating error-free datasets was neither possible due to the lack of validation techniques, nor a high priority.

@@

The OSM data precision study by \textbf{(Fan et al, 2014)} used the Douglas-Peucker algorithm, first defined by \textbf{(Douglas and Peucker, 1973)}, to reduce both building polygons to a simliar vertex count, and then proceed with locating the most likely matching vertices in the polygons. The full procedure for matching points will be presented in section 3.2.3 of this report.
The study by \textbf{(Fan et al, 2014)} also obtained a measure of the \textbf{shape accuracy} of building footprints.
While the positional accuracy accounts for the error between individual points in a polygon, the shape accuracy is a measure of how similar two polygons at a higher level of observation, regardless of relative scaling and rotation of the two polygons.
The shape accuracy between two matching buildings was quantified by using a similarity function that depends on the difference between the turning functions of matching building footprints in both datasets.
The turning function was first defined by \textbf{(Arkin et al, 1991)}, as a method for measuring the similarity of two polygons, and measures the cumulative angle of a single polygon's counter-clockwise tangent, as a function of the cumulative normalized length l.
The turning function effectively steps over the tangent of a polygon continously for a full cycle, and logs the total turning angle by adding together the angle of each turn.
It includes consideration of wether the individual turns are clockwise or counter-clockwise, and is invariant to rotation and scaling of the polygon.
Once the turning functions of two similar polygons have been obtained, the integral between them is taken as a measure of shape accuracy.

>>>>

\title{Quality Assesment of OpenStreetMap Footpath Data}
\alttitle{Kvalitetiv undersökning av OpenStreetMaps gångvägsdata}
\author{Alexander Hjelm}
\email{aljhelm@kth.se}
\supervisor{Christopher Peters}
\examiner{Jonas Beskow}
%\hostcompany{Företaget AB} % Remove this line if the project was not done at a host company
\programme{Master in Computer Science}
\school{School of Electrical Engineering and Computer Science}
\date{\today}

@@

When it comes to the quality of available data, it turns out that in practise, geodata databases without errors are rare.
Among the most common errors are missing or invalid geometry, and invalid semantics.
However, \textbf{(Biljecki et al, 2016 (2))} note that there are coming more and more sophisticated methods for automatically correcting the most common errors.
Geodata validation and correction is only an emerging field of research.
and many such datasets were usually obtained years ago, and creating error-free datasets was neither possible due to the lack of validation techniques, nor a high priority.

@@

The OSM data precision study by \textbf{(Fan et al, 2014)} used the Douglas-Peucker algorithm, first defined by \textbf{(Douglas and Peucker, 1973)}, to reduce both building polygons to a simliar vertex count, and then proceed with locating the most likely matching vertices in the polygons.
The full procedure for matching points will be presented in section 3.2.3 of this report.
The study by \textbf{(Fan et al, 2014)} also obtained a measure of the \textbf{shape accuracy} of building footprints.
While the positional accuracy accounts for the error between individual points in a polygon, the shape accuracy is a measure of how similar two polygons at a higher level of observation, regardless of relative scaling and rotation of the two polygons.
The shape accuracy between two matching buildings was quantified by using a similarity function that depends on the difference between the turning functions of matching building footprints in both datasets.
The turning function was first defined by \textbf{(Arkin et al, 1991)}, as a method for measuring the similarity of two polygons, and measures the cumulative angle of a single polygon's counter-clockwise tangent, as a function of the cumulative normalized length l.
The turning function effectively steps over the tangent of a polygon continously for a full cycle, and logs the total turning angle by adding together the angle of each turn.
It includes consideration of wether the individual turns are clockwise or counter-clockwise, and is invariant to rotation and scaling of the polygon.
Once the turning functions of two similar polygons have been obtained, the integral between them is taken as a measure of shape accuracy.
The full procedure for calculating shape accuracy will be presented in section 3.2.3 of this report.
